Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-13 automatica/paper.tex
labels, citation

\subsection{Bounded Model Checking}
We use the bounded model checker CBMC~\cite{ClarkeKL04} to model controller behaviour on digitial signals with finite
bit-precision.  
We express these controller semantics as C programs, which is CBMC's preferred input language.  
CBMC
symbolically executes every instruction in an input program by translating it to a boolean satisfiability problem.  
At
the end of this process, the entire input program is translated to a boolean satisfiability formula which is satisfiable
iff a certain property about the program holds.  
CBMC's API allows to specify these properties in the form of assertions
in the input program, and we use these properties to express that our generated controllers are stable and safe.
%\note{Do we need more details here? Should we explain e.g. SSA or give examples of how assignments, loops,
%etc. are turned into formulas? Part of Sec.~\ref{sec:errors} can probably be moved here.}

@@

\subsection{Bit-precise symbolic model checking}
As described in section~\ref{sec:preliminaries}, we use CBMC, a bit-precise bounded model checker to synthesise and verify candidate controllers. CBMC performs precisely the fixed or floating point arithmetic used in the controller, as well as the ADC/DAC conversions, according to the IEEE standards.

\subsection{Interval arithmetic over errors in numeric representation} 
We use finite-precision arithmetic to model the plant. This is an approximation that speeds up each CEGIS
iteration but necessitates a further stage where we verify that the errors introduced by the
approximation have not caused us to generate a controller that is unsafe when executed with real numbers 
for the plant. In this stage, we represent the plant using double precision floating point
and we use the Boost interval arithmetic library~\cite{} to bound the error in this representation. We use a compositional numeric library to perform the fixed point arithmetic for the controller~\cite{}. We check the controller is safe starting from each vertex state, which we have shown to be sufficient to prove safety from any initial state in the hypercube of possible initial states.

>>>>

\subsection{Bounded Model Checking}
\label{sec:BMC}
We use the bounded model checker CBMC~\cite{ClarkeKL04} to model controller behaviour on digitial signals with finite
bit-precision.  
We express these controller semantics as C programs, which is CBMC's preferred input language.  
CBMC
symbolically executes every instruction in an input program by translating it to a boolean satisfiability problem.  
At
the end of this process, the entire input program is translated to a boolean satisfiability formula which is satisfiable
iff a certain property about the program holds.  
CBMC's API allows to specify these properties in the form of assertions
in the input program, and we use these properties to express that our generated controllers are stable and safe.
%\note{Do we need more details here? Should we explain e.g. SSA or give examples of how assignments, loops,
%etc. are turned into formulas? Part of Sec.~\ref{sec:errors} can probably be moved here.}

@@

\subsection{Bit-precise symbolic model checking}
As described in section~\ref{sec:BMC}, we use CBMC, a bit-precise bounded model checker to synthesise and verify candidate controllers. CBMC performs precisely the fixed or floating point arithmetic used in the controller, as well as the ADC/DAC conversions, according to the IEEE standards.

\subsection{Interval arithmetic over errors in numeric representation} 
We use finite-precision arithmetic to model the plant. This is an approximation that speeds up each CEGIS
iteration but necessitates a further stage where we verify that the errors introduced by the
approximation have not caused us to generate a controller that is unsafe when executed with real numbers 
for the plant. In this stage, we represent the plant using double precision floating point
and we use the Boost interval arithmetic library~\cite{DBLP:journals/tcs/BronnimannMP06} to bound the error in this representation. We use a compositional numeric library to perform the fixed point arithmetic for the controller~\cite{}. We check the controller is safe starting from each vertex state, which we have shown to be sufficient to prove safety from any initial state in the hypercube of possible initial states.
